---
title: "Mice Protein Expression Data from Kaggle"
output: 
  html_document: 
    keep_md: yes
date: "2023-07-08"
---

```{r}
getwd()
```
```{r}
mice_data <- readr::read_csv("Data_Cortex_Nuclear.csv")
```
```{r}
library(tidyverse)
library(janitor)
library(skimr)
```

```{r}
mice_data_clean <- janitor::clean_names(mice_data)
mice_data_clean
```

```{r}
names(mice_data_clean) = gsub(pattern = "_n", replacement = "", x = names(mice_data_clean))
mice_data_clean
```
#NA's?
```{r}
anyNA(mice_data_clean) 
```
```{r}
is.na(mice_data_clean)
```
#^ That didn't show where the NAs occur. Take a look at the data itself, it's not complete for subjects 3426_13, 3426_14, and 3426_15. 

#Looking at classes of data
```{r}
mice_data_clean$genotype <- as.character(mice_data_clean$genotype)
mice_data_clean$treatment <- as.character(mice_data_clean$treatment)
mice_data_clean$behavior <- as.character(mice_data_clean$behavior)
mice_data_clean$class <- as.character(mice_data_clean$class)
mice_data_clean
```

#Practice pivoting longer 
```{r}
#mice_data_long <- mice_data_clean %>% 
  #pivot_longer(!mouse_id, names_to = "protein", values_to = "count") %>% 
 # group_by(mouse_id) 
#mice_data_long
```
#Try finding out some statistics about the level of expression of the proteins.
```{r}
#mice_data_long %>%
  #group_by(protein) %>%
  #summarize(mean_expression=mean(count, na.rm=T)) %>% 
  #arrange(desc(mean_expression))
```
#The protein nr2a is the most expressed in these mice. 

#Let's go back to the mice_data_clean (the wide version of the data) to investigate genotype, treatment, behavior, and class. Which protein is expressed the most in each combination of subject type (genotype, treatment, behavior, class)?
```{r}
#Genotype: control (c) or trisomy (t)
#Treatment type: memantine (m) or saline (s)
#Behavior: context-shock (CS) or shock-context (SC)
#Class: c-CS-s, c-CS-m, c-SC-s, c-SC-m, t-CS-s, t-CS-m, t-SC-s, t-SC-m
mice_data_clean %>%
  filter(genotype=="c", treatment=="m", behavior=="cs", class=="c-CS-s")
```

```{r}
mice_data_clean
```

